---
title: "Interactive R Markdown document with QR code"
author: "Andrzej Oleś"
date: "February 10, 2016"
output: html_document
runtime: shiny
---

<script type="text/javascript">
  document.addEventListener("DOMContentLoaded", function() {
  var links = document.links;
  for (var i = 0, linksLength = links.length; i < linksLength; i++)
  if (links[i].hostname != window.location.hostname)
  links[i].target = '_blank';
  });
</script>

It is possible to embed Shiny components in an R Markdown document, resulting in interactive R Markdown documents. More information on how to use these documents is available on the [Shiny](http://shiny.rstudio.com/articles/interactive-docs.html) and [R Markdown](http://rmarkdown.rstudio.com/authoring_shiny.html) websites.

Even though interactive documents don't explicitly specify an UI and a server, enabling shinyURL is still easy: simply call the function `shinyURL.server` anywhere in your document.

```{r shinyURL}
library("shinyURL")
url = shinyURL.server()
```

`shinyURL.server` returns the app's URL in form of an reactive expression. In the example above we store it under the name `url`. Rather than embedding the default UI widget provided by shinyURL, we will use this reactive expression to insert the link inline, as demonstrated in [Share this document](#share) Additionally, with the help of the R package [qrcode](https://cran.r-project.org/web/packages/qrcode/index.html) we generate a [QR code](https://en.wikipedia.org/wiki/QR_code) containing the app's URL.

## Sample Inputs and Outputs

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})

```

## Share this document {#share}

The current view state of this document can be accessed at `r output$link = renderText( url() ); textOutput("link", container = a)`, or using the QR code below.

```{r qrcode, echo=FALSE}
library(qrcode)

qrcode = reactive( t(qrcode_gen(url(), plotQRcode = FALSE, dataOutput = TRUE, softLimitFlag = FALSE)) )
nc = reactive( ncol(qrcode()) )
nr = reactive( nrow(qrcode()) )
scale = 4

renderPlot({
      opar = par(mar=c(0,0,0,0))
      on.exit( par(opar) )
      image(1L:nc(), 1L:nr(), qrcode(), xlim = 0.5 + c(0, nc()),
            ylim = 0.5 + c(nr(), 0), axes = FALSE, xlab = "", ylab = "",
            col = c("white", "black"), asp = 1)
      }, width = function() scale*nc(), height = function() scale*nr())
```
